### 2018-08-30 manuscript/manuscript.Rmd
good

---
title             : "The title"
shorttitle        : "Title"

@@

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

@@

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

>>>>

---
title             : "Backwards letters paper 2"
shorttitle        : "Title"

@@

affiliation:
  - id            : "1"
    institution   : "The University of Sydney"
  - id            : "2"
    institution   : "Konstanz Business School"

@@

abstract: |
  During natural reading of canonically-oriented English text, attention shifts from left to right.
